Deriving Random Generators via\\ Higher-Level Representations

### 2019-01-21 paper/tikz/hrep.tex
WIP

\hspace*{-4mm}
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-0.9,xscale=0.9]
%uncomment if require: \path (0,367.99999618530273); %set diagram left start at 0, and has height of 367.99999618530273

%Shape: Rectangle [id:dp9489660675592899]
\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ][fill={rgb, 255:red, 249; green, 249; blue, 249 }  ,fill opacity=1 ][line width=1]  (110,20) .. controls (110,14.48) and (114.48,10) .. (120,10) -- (420,10) .. controls (425.52,10) and (430,14.48) .. (430,20) -- (430,220) .. controls (430,225.52) and (425.52,230) .. (420,230) -- (120,230) .. controls (114.48,230) and (110,225.52) .. (110,220) -- cycle ;
%Straight Lines [id:da7051587981224026]
\draw [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1]    (270,250) .. controls (268.33,248.33) and (268.33,246.67) .. (270,245) .. controls (271.67,243.33) and (271.67,241.67) .. (270,240) .. controls (268.33,238.33) and (268.33,236.67) .. (270,235) .. controls (271.67,233.33) and (271.67,231.67) .. (270,230) .. controls (268.33,228.33) and (268.33,226.67) .. (270,225) .. controls (271.67,223.33) and (271.67,221.67) .. (270,220) .. controls (268.33,218.33) and (268.33,216.67) .. (270,215) .. controls (271.67,213.33) and (271.67,211.67) .. (270,210) .. controls (268.33,208.33) and (268.33,206.67) .. (270,205) -- (270,201) -- (270,193) ;
\draw [shift={(270,190)}, rotate = 450] [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1]    (14.21,-4.28) .. controls (9.04,-1.82) and (4.3,-0.39) .. (0,0) .. controls (4.3,0.39) and (9.04,1.82) .. (14.21,4.28)   ;

%Straight Lines [id:da6087008244886778]
\draw [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1]    (380,250) .. controls (378.33,248.33) and (378.33,246.67) .. (380,245) .. controls (381.67,243.33) and (381.67,241.67) .. (380,240) .. controls (378.33,238.33) and (378.33,236.67) .. (380,235) .. controls (381.67,233.33) and (381.67,231.67) .. (380,230) .. controls (378.33,228.33) and (378.33,226.67) .. (380,225) .. controls (381.67,223.33) and (381.67,221.67) .. (380,220) .. controls (378.33,218.33) and (378.33,216.67) .. (380,215) -- (380,211) -- (380,203) ;
\draw [shift={(380,200)}, rotate = 450] [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1]    (14.21,-4.28) .. controls (9.04,-1.82) and (4.3,-0.39) .. (0,0) .. controls (4.3,0.39) and (9.04,1.82) .. (14.21,4.28)   ;

%Shape: Rectangle [id:dp701556783783656]
\draw  [line width=1]  (230,255) .. controls (230,252.24) and (232.24,250) .. (235,250) -- (305,250) .. controls (307.76,250) and (310,252.24) .. (310,255) -- (310,275) .. controls (310,277.76) and (307.76,280) .. (305,280) -- (235,280) .. controls (232.24,280) and (230,277.76) .. (230,275) -- cycle ;

%Shape: Rectangle [id:dp033430127809365384]
\draw  [line width=1]  (340,255) .. controls (340,252.24) and (342.24,250) .. (345,250) -- (415,250) .. controls (417.76,250) and (420,252.24) .. (420,255) -- (420,275) .. controls (420,277.76) and (417.76,280) .. (415,280) -- (345,280) .. controls (342.24,280) and (340,277.76) .. (340,275) -- cycle ;
%Up Arrow [id:dp0013771056350821986]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 248; green, 231; blue, 28 }  ,fill opacity=1 ][line width=1]  (260,289.5) -- (270,280) -- (280,289.5) -- (273.5,289.5) -- (273.5,310) -- (266.5,310) -- (266.5,289.5) -- cycle ;
%Shape: Rectangle [id:dp1692119124811613]
\draw  [line width=1]  (110,310) -- (430,310) -- (430,340) -- (110,340) -- cycle ;
%Up Arrow [id:dp4999372801455]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 248; green, 231; blue, 28 }  ,fill opacity=1 ][line width=1]  (370,289.5) -- (380,280) -- (390,289.5) -- (383.5,289.5) -- (383.5,310) -- (376.5,310) -- (376.5,289.5) -- cycle ;
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (223,132.93) .. controls (223,129.02) and (219.83,125.86) .. (215.93,125.86) .. controls (212.02,125.86) and (208.86,129.02) .. (208.86,132.93) .. controls (208.86,136.83) and (212.02,140) .. (215.93,140) .. controls (219.83,140) and (223,136.83) .. (223,132.93) -- cycle ; \draw  [line width=1]  (223,132.93) -- (208.86,132.93) ; \draw  [line width=1]  (215.93,125.86) -- (215.93,140) ;
%Snip Same Side Corner Rect [id:dp11914646356873848]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (230,67.5) -- (237,60.5) -- (303,60.5) -- (310,67.5) -- (310,80.5) -- (310,80.5) -- (230,80.5) -- (230,80.5) -- cycle ;
%Shape: Rectangle [id:dp6865365415345861]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (230,80.5) -- (310,80.5) -- (310,190.5) -- (230,190.5) -- cycle ;
%Shape: Rectangle [id:dp39543698275133865]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (236.29,107.66) -- (303.21,107.66) -- (303.21,130.34) -- (236.29,130.34) -- cycle ;
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (247,75.5) .. controls (249.76,72.74) and (249.76,68.26) .. (247,65.5) .. controls (244.24,62.74) and (239.76,62.74) .. (237,65.5) .. controls (234.24,68.26) and (234.24,72.74) .. (237,75.5) .. controls (239.76,78.26) and (244.24,78.26) .. (247,75.5) -- cycle ; \draw  [line width=1]  (247,75.5) -- (237,65.5) ; \draw  [line width=1]  (247,65.5) -- (237,75.5) ;
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (277.14,143.43) .. controls (277.14,139.52) and (273.98,136.36) .. (270.07,136.36) .. controls (266.17,136.36) and (263,139.52) .. (263,143.43) .. controls (263,147.33) and (266.17,150.5) .. (270.07,150.5) .. controls (273.98,150.5) and (277.14,147.33) .. (277.14,143.43) -- cycle ; \draw  [line width=1]  (277.14,143.43) -- (263,143.43) ; \draw  [line width=1]  (270.07,136.36) -- (270.07,150.5) ;
%Shape: Rectangle [id:dp047421885346712545]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (236.08,157.66) -- (303,157.66) -- (303,180.34) -- (236.08,180.34) -- cycle ;
%Shape: Rectangle [id:dp0425475572348164]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (340,40) -- (420,40) -- (420,200) -- (340,200) -- cycle ;
%Shape: Rectangle [id:dp9247208762532781]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (345,66.37) -- (415,66.37) -- (415,89) -- (345,89) -- cycle ;
%Shape: Rectangle [id:dp8712965895636344]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (345.52,117.37) -- (414.48,117.37) -- (414.48,140) -- (345.52,140) -- cycle ;
%Shape: Rectangle [id:dp933766425327347]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (346.66,168.24) -- (413.34,168.24) -- (413.34,190.87) -- (346.66,190.87) -- cycle ;
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (387.14,103.95) .. controls (387.14,100.05) and (383.98,96.89) .. (380.07,96.89) .. controls (376.17,96.89) and (373,100.05) .. (373,103.95) .. controls (373,107.84) and (376.17,111) .. (380.07,111) .. controls (383.98,111) and (387.14,107.84) .. (387.14,103.95) -- cycle ; \draw  [line width=1]  (387.14,103.95) -- (373,103.95) ; \draw  [line width=1]  (380.07,96.89) -- (380.07,111) ;
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (387.14,152.95) .. controls (387.14,149.05) and (383.98,145.89) .. (380.07,145.89) .. controls (376.17,145.89) and (373,149.05) .. (373,152.95) .. controls (373,156.84) and (376.17,160) .. (380.07,160) .. controls (383.98,160) and (387.14,156.84) .. (387.14,152.95) -- cycle ; \draw  [line width=1]  (387.14,152.95) -- (373,152.95) ; \draw  [line width=1]  (380.07,145.89) -- (380.07,160) ;
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (333,132.93) .. controls (333,129.02) and (329.83,125.86) .. (325.93,125.86) .. controls (322.02,125.86) and (318.86,129.02) .. (318.86,132.93) .. controls (318.86,136.83) and (322.02,140) .. (325.93,140) .. controls (329.83,140) and (333,136.83) .. (333,132.93) -- cycle ; \draw  [line width=1]  (333,132.93) -- (318.86,132.93) ; \draw  [line width=1]  (325.93,125.86) -- (325.93,140) ;
%Snip Same Side Corner Rect [id:dp09931070350524518]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (120,27.48) -- (126.98,20.5) -- (193.02,20.5) -- (200,27.48) -- (200,40.45) -- (200,40.45) -- (120,40.45) -- (120,40.45) -- cycle ;
%Shape: Rectangle [id:dp6050538306488522]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (120,40.45) -- (200,40.45) -- (200,220) -- (120,220) -- cycle ;
%Shape: Rectangle [id:dp20494666512059623]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (130,67.54) -- (190,67.54) -- (190,90.17) -- (130,90.17) -- cycle ;
%Shape: Rectangle [id:dp8741156804316592]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (130,137.36) -- (190,137.36) -- (190,159.99) -- (130,159.99) -- cycle ;
%Shape: Rectangle [id:dp7972859165129229]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (130,187.24) -- (190,187.24) -- (190,209.87) -- (130,209.87) -- cycle ;
%Snip Same Side Corner Rect [id:dp44067415974317603]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (130,124.4) -- (136.98,117.41) -- (183.02,117.41) -- (190,124.4) -- (190,137.36) -- (190,137.36) -- (130,137.36) -- (130,137.36) -- cycle ;
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (147,132.22) .. controls (149.76,129.46) and (149.76,125) .. (147,122.24) .. controls (144.24,119.49) and (139.76,119.49) .. (137,122.24) .. controls (134.24,125) and (134.24,129.46) .. (137,132.22) .. controls (139.76,134.97) and (144.24,134.97) .. (147,132.22) -- cycle ; \draw  [line width=1]  (147,132.22) -- (137,122.24) ; \draw  [line width=1]  (147,122.24) -- (137,132.22) ;
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (137,35.46) .. controls (139.76,32.71) and (139.76,28.24) .. (137,25.49) .. controls (134.24,22.73) and (129.76,22.73) .. (127,25.49) .. controls (124.24,28.24) and (124.24,32.71) .. (127,35.46) .. controls (129.76,38.22) and (134.24,38.22) .. (137,35.46) -- cycle ; \draw  [line width=1]  (137,35.46) -- (127,25.49) ; \draw  [line width=1]  (137,25.49) -- (127,35.46) ;
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (167.14,103.22) .. controls (167.14,99.33) and (163.98,96.17) .. (160.07,96.17) .. controls (156.17,96.17) and (153,99.33) .. (153,103.22) .. controls (153,107.12) and (156.17,110.27) .. (160.07,110.27) .. controls (163.98,110.27) and (167.14,107.12) .. (167.14,103.22) -- cycle ; \draw  [line width=1]  (167.14,103.22) -- (153,103.22) ; \draw  [line width=1]  (160.07,96.17) -- (160.07,110.27) ;
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ][line width=1]  (167.14,173.05) .. controls (167.14,169.15) and (163.98,165.99) .. (160.07,165.99) .. controls (156.17,165.99) and (153,169.15) .. (153,173.05) .. controls (153,176.94) and (156.17,180.1) .. (160.07,180.1) .. controls (163.98,180.1) and (167.14,176.94) .. (167.14,173.05) -- cycle ; \draw  [line width=1]  (167.14,173.05) -- (153,173.05) ; \draw  [line width=1]  (160.07,165.99) -- (160.07,180.1) ;
%Down Arrow [id:dp5984296172784]
\draw  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ][fill={rgb, 255:red, 249; green, 249; blue, 249 }  ,fill opacity=1 ][line width=1]  (160,299.5) -- (165,299.5) -- (165,230) -- (175,230) -- (175,299.5) -- (180,299.5) -- (170,310) -- cycle ;
%Straight Lines [id:da30879479079788386]
\draw [color={rgb, 255:red, 249; green, 245; blue, 245 }  ,draw opacity=1 ][fill={rgb, 255:red, 249; green, 249; blue, 249 }  ,fill opacity=1 ][line width=1]    (166.25,230) -- (173.75,230) ;

%Straight Lines [id:da8667104419281686]
\draw [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1]    (190,310) .. controls (188.33,308.33) and (188.33,306.67) .. (190,305) .. controls (191.67,303.33) and (191.67,301.67) .. (190,300) .. controls (188.33,298.33) and (188.33,296.67) .. (190,295) .. controls (191.67,293.33) and (191.67,291.67) .. (190,290) .. controls (188.33,288.33) and (188.33,286.67) .. (190,285) .. controls (191.67,283.33) and (191.67,281.67) .. (190,280) .. controls (188.33,278.33) and (188.33,276.67) .. (190,275) .. controls (191.67,273.33) and (191.67,271.67) .. (190,270) .. controls (188.33,268.33) and (188.33,266.67) .. (190,265) .. controls (191.67,263.33) and (191.67,261.67) .. (190,260) .. controls (188.33,258.33) and (188.33,256.67) .. (190,255) .. controls (191.67,253.33) and (191.67,251.67) .. (190,250) .. controls (188.33,248.33) and (188.33,246.67) .. (190,245) .. controls (191.67,243.33) and (191.67,241.67) .. (190,240) .. controls (188.33,238.33) and (188.33,236.67) .. (190,235) -- (190,231) -- (190,223) ;
\draw [shift={(190,220)}, rotate = 450] [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ][line width=1]    (14.21,-4.28) .. controls (9.04,-1.82) and (4.3,-0.39) .. (0,0) .. controls (4.3,0.39) and (9.04,1.82) .. (14.21,4.28)   ;

>>>>

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1.1,xscale=1.1]
%uncomment if require: \path (0,439.4285583496094); %set diagram left start at 0, and has height of 439.4285583496094

%Right Arrow [id:dp7732858674364509]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (340,255) -- (340,195) -- (335,195) -- (345,195) -- (355,195) -- (350,195) -- (350,255) -- cycle ;
%Right Arrow [id:dp2590973168233759]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (311,190) -- (360.31,190) -- (360.31,185) -- (376,195) -- (360.31,205) -- (360.31,200) -- (311,200) -- cycle ;
%Shape: Rectangle [id:dp2141233912633571]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (231,125) -- (321,125) -- (321,255) -- (231,255) -- cycle ;
%Right Arrow [id:dp06215174722463401]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (171,161.75) -- (228.69,161.75) -- (228.69,158) -- (241,165.5) -- (228.69,173) -- (228.69,169.25) -- (171,169.25) -- cycle ;
%Right Arrow [id:dp6766910698477273]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (171,196.75) -- (228.69,196.75) -- (228.69,193) -- (241,200.5) -- (228.69,208) -- (228.69,204.25) -- (171,204.25) -- cycle ;
%Right Arrow [id:dp3196923724356615]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (171,230.75) -- (228.69,230.75) -- (228.69,227) -- (241,234.5) -- (228.69,242) -- (228.69,238.25) -- (171,238.25) -- cycle ;
%Right Arrow [id:dp0360549353694295]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (431,190) -- (480.31,190) -- (480.31,185) -- (496,195) -- (480.31,205) -- (480.31,200) -- (431,200) -- cycle ;
%Shape: Rectangle [id:dp2934677500856828]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (496,125) -- (596,125) -- (596,255) -- (496,255) -- cycle ;
%Straight Lines [id:da7152551743774183]
\draw    (558.5,207.5) -- (568.5,217) ;

%Straight Lines [id:da3837250992572381]
\draw    (558.5,207.5) -- (548.5,222.5) ;

%Straight Lines [id:da8680015881494354]
\draw    (568.5,217) -- (558.08,227.11) ;

%Straight Lines [id:da7327748351239962]
\draw    (548.5,222.5) -- (553.11,242.11) ;

%Straight Lines [id:da007641890318750955]
\draw    (568.5,217) -- (566.5,235) ;

%Straight Lines [id:da995333968066006]
\draw    (568.11,146.11) -- (578.11,157.89) ;

%Straight Lines [id:da015868138489393502]
\draw    (568.11,146.11) -- (562.5,157) ;

%Straight Lines [id:da7302160362706243]
\draw    (562.5,157) -- (574.5,168.5) ;

%Straight Lines [id:da46726020734917606]
\draw    (562.5,157) -- (559.5,170.5) ;

%Straight Lines [id:da4868124795808251]
\draw    (574.5,168.5) -- (571.5,181) ;

%Straight Lines [id:da6000768704792225]
\draw    (521.89,188.11) -- (529.5,196.5) ;

%Straight Lines [id:da9056461286434507]
\draw    (521.89,188.11) -- (518.89,202.11) ;

%Straight Lines [id:da5328270203547492]
\draw    (529,178.13) -- (533.5,188) ;

%Straight Lines [id:da38335809761139505]
\draw    (521.5,165.63) -- (528.5,177.5) ;

%Straight Lines [id:da39066239946769477]
\draw    (513.11,177.11) -- (521.89,188.11) ;

%Straight Lines [id:da6974822807110195]
\draw    (513.11,177.11) -- (511.5,190.5) ;

%Straight Lines [id:da06361852802164258]
\draw    (521.5,165.63) -- (513.11,177.11) ;

%Snip Single Corner Rect [id:dp4647891928859724]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (55,125) -- (161.34,125) -- (175,138.66) -- (175,255) -- (55,255) -- cycle ;
%Shape: Rectangle [id:dp3811163355625795]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (376.5,125) -- (436.5,125) -- (436.5,255) -- (376.5,255) -- cycle ;
%Shape: Ellipse [id:dp7838604577819246]
\draw   (385,238.16) .. controls (385,231.62) and (393.95,226.32) .. (405,226.32) .. controls (416.05,226.32) and (425,231.62) .. (425,238.16) .. controls (425,244.7) and (416.05,250) .. (405,250) .. controls (393.95,250) and (385,244.7) .. (385,238.16) -- cycle ;
%Shape: Circle [id:dp36073479073960346]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (408.16,230.53) .. controls (408.16,229.36) and (409.1,228.42) .. (410.26,228.42) .. controls (411.43,228.42) and (412.37,229.36) .. (412.37,230.53) .. controls (412.37,231.69) and (411.43,232.63) .. (410.26,232.63) .. controls (409.1,232.63) and (408.16,231.69) .. (408.16,230.53) -- cycle ;
%Shape: Circle [id:dp8080098028480491]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (397.53,245.16) .. controls (397.53,244) and (398.47,243.05) .. (399.63,243.05) .. controls (400.79,243.05) and (401.74,244) .. (401.74,245.16) .. controls (401.74,246.32) and (400.79,247.26) .. (399.63,247.26) .. controls (398.47,247.26) and (397.53,246.32) .. (397.53,245.16) -- cycle ;
%Shape: Circle [id:dp12076525384098513]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (415.37,240.95) .. controls (415.37,239.78) and (416.31,238.84) .. (417.47,238.84) .. controls (418.64,238.84) and (419.58,239.78) .. (419.58,240.95) .. controls (419.58,242.11) and (418.64,243.05) .. (417.47,243.05) .. controls (416.31,243.05) and (415.37,242.11) .. (415.37,240.95) -- cycle ;
%Shape: Ellipse [id:dp5212893057388461]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (401.53,232.32) .. controls (401.53,231.15) and (402.47,230.21) .. (403.63,230.21) .. controls (404.79,230.21) and (405.74,231.15) .. (405.74,232.32) .. controls (405.74,233.48) and (404.79,234.42) .. (403.63,234.42) .. controls (402.47,234.42) and (401.53,233.48) .. (401.53,232.32) -- cycle ;
%Shape: Circle [id:dp23843560123656338]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (406.79,241) .. controls (406.79,239.84) and (407.73,238.89) .. (408.89,238.89) .. controls (410.06,238.89) and (411,239.84) .. (411,241) .. controls (411,242.16) and (410.06,243.11) .. (408.89,243.11) .. controls (407.73,243.11) and (406.79,242.16) .. (406.79,241) -- cycle ;
%Shape: Ellipse [id:dp4809698571086918]
\draw   (385,197.5) .. controls (385,190.6) and (393.95,185) .. (405,185) .. controls (416.05,185) and (425,190.6) .. (425,197.5) .. controls (425,204.4) and (416.05,210) .. (405,210) .. controls (393.95,210) and (385,204.4) .. (385,197.5) -- cycle ;
%Shape: Triangle [id:dp24226788884090933]
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (392.5,195) -- (395,200) -- (390,200) -- cycle ;
%Shape: Triangle [id:dp5291497962409548]
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (402.5,190) -- (405,195) -- (400,195) -- cycle ;
%Shape: Triangle [id:dp5917974674439683]
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (412.5,190) -- (415,195) -- (410,195) -- cycle ;
%Shape: Triangle [id:dp29519879870465426]
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (405,200) -- (407.5,205) -- (402.5,205) -- cycle ;
%Shape: Triangle [id:dp6574937894365762]
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (415,199) -- (417.5,204) -- (412.5,204) -- cycle ;
%Shape: Ellipse [id:dp8770682879482239]
\draw   (385,157.81) .. controls (385,150.74) and (394.14,145) .. (405.42,145) .. controls (416.69,145) and (425.83,150.74) .. (425.83,157.81) .. controls (425.83,164.89) and (416.69,170.63) .. (405.42,170.63) .. controls (394.14,170.63) and (385,164.89) .. (385,157.81) -- cycle ;
%Shape: Circle [id:dp5633637507570923]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (392.79,236.89) .. controls (392.79,235.73) and (393.73,234.79) .. (394.89,234.79) .. controls (396.06,234.79) and (397,235.73) .. (397,236.89) .. controls (397,238.06) and (396.06,239) .. (394.89,239) .. controls (393.73,239) and (392.79,238.06) .. (392.79,236.89) -- cycle ;
%Shape: Rectangle [id:dp853277524439841]
\draw  [fill={rgb, 255:red, 65; green, 117; blue, 5 }  ,fill opacity=1 ] (397,160.63) -- (402,160.63) -- (402,164.63) -- (397,164.63) -- cycle ;
%Shape: Rectangle [id:dp26443574867732256]
\draw  [fill={rgb, 255:red, 65; green, 117; blue, 5 }  ,fill opacity=1 ] (393,150.63) -- (398,150.63) -- (398,154.63) -- (393,154.63) -- cycle ;
%Shape: Rectangle [id:dp3935753971313367]
\draw  [fill={rgb, 255:red, 65; green, 117; blue, 5 }  ,fill opacity=1 ] (410,148.63) -- (415,148.63) -- (415,152.63) -- (410,152.63) -- cycle ;
%Shape: Rectangle [id:dp5931653318550618]
\draw  [fill={rgb, 255:red, 65; green, 117; blue, 5 }  ,fill opacity=1 ] (410,162.63) -- (415,162.63) -- (415,166.63) -- (410,166.63) -- cycle ;
%Shape: Rectangle [id:dp7233342352369083]
\draw  [fill={rgb, 255:red, 65; green, 117; blue, 5 }  ,fill opacity=1 ] (403,154.63) -- (408,154.63) -- (408,158.63) -- (403,158.63) -- cycle ;
%Shape: Ellipse [id:dp9722655375449147]
\draw   (540.17,225) .. controls (540.17,211.19) and (548.19,200) .. (558.08,200) .. controls (567.98,200) and (576,211.19) .. (576,225) .. controls (576,238.81) and (567.98,250) .. (558.08,250) .. controls (548.19,250) and (540.17,238.81) .. (540.17,225) -- cycle ;
%Shape: Ellipse [id:dp9371514401907413]
\draw  [color={rgb, 255:red, 74; green, 74; blue, 74 }  ,draw opacity=1 ] (504,184) .. controls (504,170.19) and (512.02,159) .. (521.92,159) .. controls (531.81,159) and (539.83,170.19) .. (539.83,184) .. controls (539.83,197.81) and (531.81,209) .. (521.92,209) .. controls (512.02,209) and (504,197.81) .. (504,184) -- cycle ;
%Shape: Ellipse [id:dp26883422845191607]
\draw   (551,165) .. controls (551,151.19) and (559.02,140) .. (568.92,140) .. controls (578.81,140) and (586.83,151.19) .. (586.83,165) .. controls (586.83,178.81) and (578.81,190) .. (568.92,190) .. controls (559.02,190) and (551,178.81) .. (551,165) -- cycle ;
%Shape: Rectangle [id:dp5872203962807194]
\draw  [fill={rgb, 255:red, 65; green, 117; blue, 5 }  ,fill opacity=1 ] (519,163.63) -- (524,163.63) -- (524,167.63) -- (519,167.63) -- cycle ;
%Shape: Circle [id:dp7605266721377453]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (511,177.11) .. controls (511,175.94) and (511.94,175) .. (513.11,175) .. controls (514.27,175) and (515.21,175.94) .. (515.21,177.11) .. controls (515.21,178.27) and (514.27,179.21) .. (513.11,179.21) .. controls (511.94,179.21) and (511,178.27) .. (511,177.11) -- cycle ;
%Shape: Triangle [id:dp4125869850828281]
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (511.5,188) -- (514,193) -- (509,193) -- cycle ;
%Shape: Triangle [id:dp09394805352485558]
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (528.5,175) -- (531,180) -- (526,180) -- cycle ;
%Shape: Circle [id:dp7834832784546726]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (516.79,202.11) .. controls (516.79,200.94) and (517.73,200) .. (518.89,200) .. controls (520.06,200) and (521,200.94) .. (521,202.11) .. controls (521,203.27) and (520.06,204.21) .. (518.89,204.21) .. controls (517.73,204.21) and (516.79,203.27) .. (516.79,202.11) -- cycle ;
%Shape: Rectangle [id:dp18557164533567394]
\draw  [fill={rgb, 255:red, 65; green, 117; blue, 5 }  ,fill opacity=1 ] (531,186) -- (536,186) -- (536,190) -- (531,190) -- cycle ;
%Shape: Circle [id:dp8025931154410937]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (519.79,188.11) .. controls (519.79,186.94) and (520.73,186) .. (521.89,186) .. controls (523.06,186) and (524,186.94) .. (524,188.11) .. controls (524,189.27) and (523.06,190.21) .. (521.89,190.21) .. controls (520.73,190.21) and (519.79,189.27) .. (519.79,188.11) -- cycle ;
%Shape: Triangle [id:dp1239939418024707]
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (529.5,194) -- (532,199) -- (527,199) -- cycle ;
%Shape: Circle [id:dp8812473863475445]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (566,146.11) .. controls (566,144.94) and (566.94,144) .. (568.11,144) .. controls (569.27,144) and (570.21,144.94) .. (570.21,146.11) .. controls (570.21,147.27) and (569.27,148.21) .. (568.11,148.21) .. controls (566.94,148.21) and (566,147.27) .. (566,146.11) -- cycle ;
%Shape: Circle [id:dp7598993443376705]
\draw  [color={rgb, 255:red, 0; green, 0; blue, 0 }  ,draw opacity=1 ][fill={rgb, 255:red, 255; green, 0; blue, 0 }  ,fill opacity=1 ] (576,157.89) .. controls (576,156.73) and (576.94,155.79) .. (578.11,155.79) .. controls (579.27,155.79) and (580.21,156.73) .. (580.21,157.89) .. controls (580.21,159.06) and (579.27,160) .. (578.11,160) .. controls (576.94,160) and (576,159.06) .. (576,157.89) -- cycle ;
%Shape: Rectangle [id:dp3435681036136593]
\draw  [fill={rgb, 255:red, 65; green, 117; blue, 5 }  ,fill opacity=1 ] (560,155) -- (565,155) -- (565,159) -- (560,159) -- cycle ;
%Shape: Triangle [id:dp4971718332882904]
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (559.5,168) -- (562,173) -- (557,173) -- cycle ;
%Shape: Triangle [id:dp8772068767151546]
\draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (574.5,166) -- (577,171) -- (572,171) -- cycle ;
%Shape: Rectangle [id:dp5389313915531764]
